---
title: "Appendices"
---

```{r, libraries, echo=FALSE, warning=FALSE, message=FALSE}
# Packages to be used in the below document.

library("tidyverse")
library("kableExtra")


## I am choosing to use `kableExtra` for the tables. It makes for better PDF output tables as opposed to the `gt` package is better suited for HTML outputs.
```

# Appendix 1 -- Proposed Timeline

```{mermaid}
gantt
title Systematic Review Screening Timeline
dateFormat  YYYY-MM-DD


section  Corpus Training and Screening

Reviewer training I             :active, c1, 2023-03-14, 1d
Reviewer training II            :active, c2, 2023-03-21, 1d
Establising concordance         :crit, milestone, c3, after c2, 2d
Title/Abstract screening        :c4, after c3, 14d
Full-text screening             :c5, after c4, 14d
```



# Appendix 2 --  Databases and Search Terms

## Databases Searched

The following sections detail the databases search strategies implemented to extract citations and references in support of the systematic review.

```{r, tablea2a, warning=FALSE, message=FALSE, echo=FALSE}

t1 <- read_csv("data/a2table1.csv") %>%
  tibble()

gt1 <- kable(t1,
             caption = "Table 01 - Databases Searched for CMM Systematic Review",
             col.names = c("Database Interface", "Database Name", "Date of Search", "Database Update", "Searchers")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"),
                full_width = F,
                font_size = 10) %>%
  footnote(symbol = c("Search strategies were developed between November 2023 and February 2023.", "The final database search was performed on March 20, 203."))

 gt1

```


### MEDLINE Using PubMed

The below outlines the search strategy developed for MEDLINE via [PubMED](https://www.PubMed.gov)

```{r, tablea2b, warning=FALSE, message=FALSE, echo=FALSE}

t2 <- read_csv("data/a2table2.csv") %>%
  tibble()

gt2 <- kable(t2, 
             caption = "Table 02 - MEDLINE (PubMed) search strategy",
             col.names = c("Search Stages", "Search Terms")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), 
                font_size = 10,
                full_width = F) %>%
  footnote(symbol = c("Database: MEDLINE", "Interface: PubMED(NLM)", "Date Range: Jan. 2010 - Mar. 2023", "Pub Types: Peer reviewed", "Filter source: N/A" ))

gt2
```


### Cumulative Index to Nursing and Allied Health Literature (CINAHL)

The below outlines the search strategy developed for the [CINAHL) Database](https://search.ebscohost.com)

```{r, tablea2c, warning=FALSE, message=FALSE, echo=FALSE}

t3 <- read_csv("data/a2table3.csv") %>%
  tibble()

gt3 <- kable(t3, 
             caption = "Table 03 - Cumulative Index to Nursing and Allied Health Literature (CINAHL)",
             col.names = c("Search Stages", "Search Terms")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), 
                font_size = 10,
                full_width = F) %>%
  footnote(symbol = c("Database: CINAHL", "Interface: Cochrane Website", "Date Range: Jan. 2010 - Mar. 2023", "Pub Types: Peer reviewed", "Filter source: N/A" ))

gt3
```


### Cochrane Library

The below outlines the search strategy developed for the [Cochrane Library](https://www.PubMed.gov)

```{r, tablea2d, warning=FALSE, message=FALSE, echo=FALSE}

t4 <- read_csv("data/a2table4.csv") %>%
  tibble()

gt4 <- kable(t4, 
             caption = "Table 04x - Cochrane Library search strategy",
             col.names = c("Search Stages", "Search Terms")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), 
                font_size = 10,
                full_width = F) %>%
  footnote(symbol = c("Database: Cochrane Library (CDSR, CENTRAL, CMR, DARE, EED, HTA)", "Interface: Cochrane Website", "Date Range: Jan. 2010 - Mar. 2023", "Pub Types: Peer reviewed", "Filter source: N/A" ))

gt4
```


### EMBASE

The below outlines the search strategy developed for the (EMBASE Database)(https://www.embase.com/landing?status=grey)


```{r, tablea2e, warning=FALSE, message=FALSE, echo=FALSE}

t5 <- read_csv("data/a2table5.csv") %>%
  tibble()

gt5 <- kable(t5, 
             caption = "Table 04 - EMBASE/EMTREE Search Strategy",
             col.names = c("Search Stages", "Search Terms")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), 
                font_size = 10,
                full_width = F) %>%
  footnote(symbol = c("Database: EMBASE", "Interface: Elsevier", "Date Range: Jan. 2010 - Mar. 2023", "Pub Types: Peer reviewed", "Filter source: N/A" ))

gt5
```


# Appendix 3

The below outlines the PRISMA 

![PRISMA Chart of Systematic Review^[Haddaway et al. (2022)]](images/cmmsr_prisma.svg){fig-align="center" width=65%}

## PRISMA Chart Details

### Specific Database Results

-   MEDLINE(PubMed), 108;
-   CINAHL, 41;
-   Cochrane Library, 68;
-   EMBASE, 21


### Exclusion Reasons

-   Wrong intervention (not CMM), xxx;
-   Wrong outcomes (see protocol), xxx;
-   Wrong language (not English), xxx;
-   Wrong country/setting (not USA), xxx;
-   Wrong population (not Hypertensive/pharmacist), xxx;
-   Wrong study type (see protocol), xxx;
-   Wrong period (not after 2010), xxx;

# Appendix 4 - Establishing Concordance

```{r, message=FALSE,warning=FALSE, echo=FALSE}
library("tidyverse")
library("readr")

```

The total number of citations in our corpus is 217 (on March 18, 2023). After a removal of ducplicates. See PRISMA chart in Appendix.
The *Cochrane Handbook for Systematic Reviews of Interventions* suggests that we use approximate 10 percent of the corpus to estimate inter-rater reliability (IRR). Therefore, we created a sequential ID variable for alll the citations in our corpus (N = 217). From there we used a random number generator to select 22 ($\approx$ 10%)

Using a random integer genearator, based on the ID column/ variable in our corpus ([Random.org](https://www.random.org)), we generated 22 random numbers between 1 and 217. Where 

```{r, warning=FALSE, message=FALSE, echo=FALSE}

af1 <- read_csv("data/2023titlesabstracts.csv")

af2 <- af1 %>%
  filter(ID %in% c("95", "202", "124", "194", "184", "13", "2", "187", "153", "115", "86", "192", "33", "210", "196", "91", "111", "99", "1", "207", "103", "7")) %>%
  select("ID", "Publication Year", "Author", "Title", "Url", "DOI", "Extra")

write_csv(af2, "data/202303concordance.csv")

```

## Concordance Established

There was a delay in establishing concordance. We had had to conduct two training sessions to make up for disagreements between the screeners.

### Kappa after training one

After the first training session, the team (a total of four raters) established a **Fleiss' Kappa of 0.35**. Which demonstrates poor agreement. Attempting to move forward given that statistic will create problems. For instance, we may miss critical citations and references for full-text review and for data extraction. See calculations below.

```{r, warning=FALSE, message=FALSE}
## Library

library(tidyverse)
library(irr)

## Data

t1 <- read_csv("data/kappa/irr_data1.csv")

## Light's Kappa works for instances with more than two raters.

kappam.light(t1[, 2:5])

## As does the Fliess's Kappa.

kappam.fleiss(t1[, 2:5])


```



### Kappa after training two

After the second training session, the team (a total of five raters) established a **Fleiss' Kappa of 0.75**. This finding demonstrates very good agreement, strong enough to move forward. See calculations below. 


```{r, warning=FALSE, message=FALSE}

## Data

t2 <- read_csv("data/kappa/irr_data2.csv")

## Light's Kappa works for instances with more than two raters.

kappam.light(t2[, 2:6])

## As does the Fleiss's Kappa.

kappam.fleiss(t2[, 2:6])


```


IRR is established on April 11, 2023. The team is then moved onto Title/ Abstract screening within the SysRev platform.



